---
title: Arthropod associations with residual dry matter and foundations shrubs in California
  desert ecosystems
output:
    rmdformats::readthedown:
      collapsed: false
      highlight: kate
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(purrr)
library(tidyr)
library(ggthemes)
library(glmmTMB)
library(ggpubr)
library(performance)
library(gridExtra)
```
***

Pitfall traps were deployed along an aridity gradient in California to measure associations of ground-dwelling arthropods with foundation shrubs, and to assess the ability of residual dry matter (RDM) as an indicator of arthropod community structure.

***

```{r}
env <- read.csv("clean_data/cov.csv")
comm <- read.csv("clean_data/comm.csv")
rdm <- read.csv("clean_data/veg_covariates.csv")
rdm <- filter(rdm, Microsite != "larrea")
eph <- filter(env)
sum(eph$abun)
str(eph)
eph$Microsite <- as.factor(eph$Microsite)
rdm$Microsite <- as.factor(rdm$Microsite)
eph$Microsite <- relevel(eph$Microsite, ref = "open")
rdm$Microsite <- relevel(rdm$Microsite, ref = "open")

se <- function(x) sd(x, na.rm = TRUE)/sqrt(length(x)) ## SE

rii <- read.csv("clean_data/rii.csv")
indrii <- read.csv("clean_data/rii_individual.csv")

effect <- dplyr::select(rii, site, ESI,Max,arid)

eph <- left_join(eph, effect, by = "site")
eph <- distinct(eph)

rdm <- left_join(rdm, effect, by = "site")
rdm <- distinct(rdm)

#env <- left_join(env, effect, by = "site")
#env <- distinct(env)

eph.abun <- filter(eph, abun < 350)
eph.abun <- distinct(eph.abun)

eph %>% group_by(Region) %>% summarise(sum = sum(abun))
```


# EDA

The sites are sorted by aridity - from most arid to least arid.




## Residual dry matter
```{r}
ggplot(rdm, aes(Microsite, RDM)) + geom_boxplot() + facet_grid(~reorder(site, arid))+ theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

## Does shrub size influence RDM?
```{r}
ggplot(rdm, aes(x, RDM)) + geom_smooth() + facet_grid(~reorder(site, arid)) + xlab("Shrub Width")+ theme_classic()

ggplot(rdm, aes(z, RDM)) + geom_smooth() + facet_grid(~reorder(site, arid)) + xlab("Shrub Height")+ theme_classic()

```

## Insect morphospecies richness
```{r}
ggplot(eph, aes(Species, fill = Microsite)) + geom_density(alpha = 0.7) + facet_grid(~reorder(site, arid))+ theme_classic()

ggplot(eph, aes(RDM, Species)) + geom_smooth(method = lm) + geom_point() + theme_classic()


ggplot(eph, aes(Microsite, Species)) + geom_boxplot() + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))


ggplot(eph, aes(RDM, Species, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic()

ggplot(eph, aes(RDM, Species, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic() + facet_grid(~Region)

```


## Insect abundance
There is one sample with 1200 insects in it, almost all ants that really throws everything off. 
```{r}
eph %>% filter(abun < 350) %>% ggplot(aes(abun, fill = Microsite)) + geom_density(alpha = 0.7) + facet_grid(~reorder(site, arid))+ theme_classic()

ggplot(filter(eph, abun <350), aes(Microsite, abun)) + geom_boxplot() + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(filter(eph, abun <350), aes(Microsite, abun)) + geom_boxplot() + facet_grid(~Region) + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(filter(eph, abun < 350), aes(RDM, abun)) + geom_smooth(method = lm) + geom_point() + theme_classic()

ggplot(filter(eph, abun < 350), aes(RDM, abun, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic()

ggplot(filter(eph, abun < 350), aes(RDM, abun, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic() + facet_grid(~Region)
```





## Site level RII 
### Residual dry matter

```{r}

ggplot(rii, aes(arid, average, color = response)) + geom_errorbar(aes(arid, ymin = average - error, ymax = average + error)) + geom_point() + geom_jitter() 
ggplot(rii, aes(arid, average, color = response)) + geom_smooth(method = lm)

```


## Individual RII (rdm)

```{r}
ggplot(indrii, aes(site, rii)) + geom_boxplot()
ggplot(indrii, aes(x, rii)) + geom_point() + geom_smooth(method = lm) + xlab("Shrub Width")
```

# Counts and summaries
## Simple counts
```{r}
arth <- read.csv("clean_data/arth_long.csv")
arth.eph <- filter(arth, Microsite != "larrea")

sum(arth.eph$Quantity)

ants <- filter(arth.eph, Family == "Formicidae") 
sum(ants$Quantity)
ants %>% count(highest.rtu)



mean(eph.abun$abun)
sum(eph.abun$abun)
sd(eph.abun$abun)

order <- arth.eph %>% group_by(Order) %>% summarise(sum = sum(Quantity))
sum(order$sum)

beetles <- filter(arth.eph, Order == "Coleoptera")
beetles %>% count(highest.rtu)
fam <- arth.eph %>% group_by(Family) %>% summarise(sum = sum(Quantity))

#how many plots contain green veg

#eph %>% count(green.cov == 0)

```

# Models

## Drivers of arthropod abundance

```{r}

eph.abun$x[is.na(eph.abun$x == TRUE)] <- 0
eph$x[is.na(eph$x == TRUE)] <- 0
m1 <- glmmTMB(abun ~ Microsite + RDM + rdm.cov +  arid + ESI + (1|site), family = "poisson", data = eph.abun)
#summary(m1)
#looks overdispersed
check_overdispersion(m1)

m1.nb <- glmmTMB(abun ~ Microsite + RDM + rdm.cov + arid + ESI +(1|site), family = "nbinom2", data = eph.abun)
summary(m1.nb)
m1.nb1 <- glmmTMB(abun ~ Microsite + RDM + rdm.cov +  arid + ESI + (1|site), family = "nbinom1", data = eph.abun)

AIC(m1, m1.nb, m1.nb1)

#nbinom2 best family

#test each rdm interaction

m2 <- glmmTMB(abun ~ Microsite * RDM + rdm.cov  + arid + ESI + (1|site), family = "nbinom2", data = eph.abun)
summary(m2)
m3 <- glmmTMB(abun ~ Microsite * rdm.cov + RDM + arid + ESI + (1|site), family = "nbinom2", data = eph.abun)
summary(m3)

AIC(m1.nb, m2, m3)
#interactions are non-significant and do not improve the model. Dropping.
anova(m1.nb, m2)
anova(m1.nb, m3)
check_collinearity(m1.nb)


summary(m1.nb)
knitr::kable(car::Anova(m1.nb, type = 2))
```

## Insect morphospecies richness

```{r}

m4 <- glmmTMB(Species ~ Microsite + RDM + rdm.cov +  arid + ESI + (1|site), family = "nbinom2", data = eph)
summary(m4)

#nb models don't coverge -> likely suggests overdispersion not an issue but should add a formal check

eph <- filter(eph, Microsite != "larrea")
m4.p <- glmmTMB(Species ~ Microsite+RDM + rdm.cov +  arid + ESI +(1|site), family = "poisson", data = eph)
summary(m4.p)
check_overdispersion(m4.p)

#wow wow, I can actually use a poisson model 

#check each interaction

m5 <- glmmTMB(Species ~ Microsite * RDM + rdm.cov +  arid + ESI + (1|site), family = "poisson", data = eph)
summary(m5)

m6 <- glmmTMB(Species ~ Microsite * rdm.cov + RDM +  arid + ESI + (1|site), family = "poisson", data = eph)
summary(m6)

m7 <- glmmTMB(Species ~ Microsite * ESI+ rdm.cov + RDM +  arid + (1|site), family = "poisson", data = eph)

AIC(m4.p, m5, m6)
anova(m4.p, m5)
anova(m4.p, m6)
#no interactions 

check_collinearity(m4.p)
summary(m4.p)
knitr::kable(car::Anova(m4.p, type = 2))


## Richness no singletons

m1nos <- glmmTMB(Species.nos ~ Microsite+RDM + rdm.cov +  arid + ESI +(1|site), family = "poisson", data = eph)
summary(m1nos)
knitr::kable(car::Anova(m1nos, type = 2))
check_overdispersion(m1nos)

```
## Influence of shrub size

```{r, shrub size}

#redo models
#shrub microsite only
shr <- filter(eph, Microsite == "ephedra")

m1.shr <- glmmTMB(Species ~ x + z + (1|site), family = "poisson", data = shr)
summary(m1.shr)
knitr::kable(car::Anova(m1.shr, type = 2))

shr.abun <- filter(shr, abun < 350)
m2.shr <- glmmTMB(abun ~ x + z + (1|site), family = "nbinom2", data = shr.abun)
summary(m2.shr)
knitr::kable(car::Anova(m2.shr, type = 2))
```

# RII
Data wrangling and calculations for RII are in RII.R


Bootstrap the mean and 95% CI for RII rdm biomass and rdm cover. These calculations are made at the individual level (n = 30 for each of nine sites) and the RII represents all nine sites
```{r}
shapiro.test(indrii$rii)
t.test(indrii$rii)
#not normal though

library(boot)
bootmean <- function(d, i) mean(d[i])

#rdm biomass

RDM.rii <- boot(indrii$rii, bootmean, R=10000, stype ="i")
ci.RDM.rii <- boot.ci(RDM.rii)
bca.RDM <- ci.RDM.rii$bca

#rdm cover

rii.cover <- read.csv("clean_data/rii_individual_rdmcover.csv")
str(rii.cover)
mean(rii.cover$rii)

cover.rii <- boot(rii.cover$rii, bootmean, R=1000, stype ="i")
ci.cover.rii <- boot.ci(cover.rii)
bca.cover <- ci.cover.rii$bca
t.test(rii.cover$rii)
```


```{r}
site.rii <- read.csv("clean_data/rii.csv")
#want to make a plot of site level rii vs average rii

site.rii <- dplyr::select(site.rii, 3:6, 13, 14, ESI, arid, Max)

#for each site, calculate the mean RDM biomass and cover for the whole site and also just under shrubs

#need to fix this
site.rii <- rdm %>% dplyr::select(site, RDM, rdm.cov) %>% group_by(site) %>% summarise(mean.rdm.biomass = mean(RDM), mean.rdm.cov = mean(rdm.cov)) %>% right_join(., site.rii, by = "site")

site.rii <- rdm %>% filter(Microsite == "ephedra") %>% dplyr::select(site, RDM, rdm.cov) %>% group_by(site) %>% summarise(shr.rdm.biomass = mean(RDM), shr.rdm.cov = mean(rdm.cov)) %>% right_join(., site.rii, by = "site")


```

## Correlations
```{r}

#relative effects
rel.rii <- pivot_wider(site.rii, site, names_from = response, values_from = average)

cor.test(rel.rii$richness, rel.rii$rdm)
cor.test(rel.rii$richness, rel.rii$cov)

cor.test(rel.rii$abun, rel.rii$rdm)
cor.test(rel.rii$abun, rel.rii$cov)

cor.test(rel.rii$rdm, rel.rii$cov)
cor.test(rel.rii$abun, rel.rii$richness)



#environmental: aridity and stress
site.rii %>% filter(response == "richness") %>% cor.test(~ESI + average, data =.)


m <- site.rii %>% filter(response == "richness") %>% lm(average ~ ESI,.)
summary(m)

site.rii %>% filter(response == "richness") %>% cor.test(~arid + average, data =.)
site.rii %>% filter(response == "richness") %>% cor.test(~Max + average, data =.)

site.rii %>% filter(response == "richness") %>% cor.test(~shr.rdm.biomass + average, data =.)
site.rii %>% filter(response == "richness") %>% cor.test(~shr.rdm.cov + average, data =.)
site.rii %>% filter(response == "richness") %>% cor.test(~mean.rdm.biomass + average, data =.)
site.rii %>% filter(response == "richness") %>% cor.test(~mean.rdm.cov + average, data =.)


site.rii %>% filter(response == "abun") %>% cor.test(~ESI + average, data =.)
site.rii %>% filter(response == "abun") %>% cor.test(~arid + average, data =.)
site.rii %>% filter(response == "abun") %>% cor.test(~Max + average, data =.)
site.rii %>% filter(response == "abun") %>% cor.test(~shr.rdm.biomass + average, data =.)
site.rii %>% filter(response == "abun") %>% cor.test(~shr.rdm.cov + average, data =.)
site.rii %>% filter(response == "abun") %>% cor.test(~mean.rdm.biomass + average, data =.)
site.rii %>% filter(response == "abun") %>% cor.test(~mean.rdm.cov + average, data =.)


site.rii %>% filter(response == "rdm") %>% cor.test(~ESI + average, data =.)
site.rii %>% filter(response == "rdm") %>% cor.test(~arid + average, data =.)

m <- site.rii %>% filter(response == "rdm") %>% lm(average~arid, data =.)
summary(m)

site.rii %>% filter(response == "rdm") %>% cor.test(~Max + average, data =.)
site.rii %>% filter(response == "rdm") %>% cor.test(~shr.rdm.biomass + average, data =.)
site.rii %>% filter(response == "rdm") %>% cor.test(~shr.rdm.cov + average, data =.)
site.rii %>% filter(response == "rdm") %>% cor.test(~mean.rdm.biomass + average, data =.)
site.rii %>% filter(response == "rdm") %>% cor.test(~mean.rdm.cov + average, data =.)

site.rii %>% filter(response == "cov") %>% cor.test(~ESI + average, data =.)
site.rii %>% filter(response == "cov") %>% cor.test(~arid + average, data =.)
site.rii %>% filter(response == "cov") %>% cor.test(~Max + average, data =.)
site.rii %>% filter(response == "cov") %>% cor.test(~shr.rdm.biomass + average, data =.)
site.rii %>% filter(response == "cov") %>% cor.test(~shr.rdm.cov + average, data =.)
site.rii %>% filter(response == "cov") %>% cor.test(~mean.rdm.biomass + average, data =.)
site.rii %>% filter(response == "cov") %>% cor.test(~mean.rdm.cov + average, data =.)




site.rii %>% filter(response == "rdm") %>% cor.test(~ESI+ mean.rdm.biomass, data =.)

m2 <- site.rii %>% filter(response == "rdm") %>% lm(mean.rdm.biomass ~ ESI, data =.) 
summary(m2)
  
site.rii %>% filter(response == "rdm") %>% cor.test(~arid+ mean.rdm.biomass, data =.)
site.rii %>% filter(response == "rdm") %>% cor.test(~ESI+ mean.rdm.cov, data =.)
site.rii %>% filter(response == "rdm") %>% cor.test(~arid+ mean.rdm.cov, data =.)
site.rii %>% filter(response == "rdm") %>% cor.test(~ESI+ shr.rdm.biomass, data =.)
site.rii %>% filter(response == "rdm") %>% cor.test(~arid+ shr.rdm.biomass, data =.)
site.rii %>% filter(response == "rdm") %>% cor.test(~ESI+ shr.rdm.cov, data =.)
site.rii %>% filter(response == "rdm") %>% cor.test(~arid+ shr.rdm.cov, data =.)


ggplot(filter(rii,response == "abun"), aes(reorder(site, arid), arid)) + geom_bar(stat="identity")
      

```


# Figures
## Figure 1

```{r}
#richness
lbls <- read.csv("clean_data/sitelabels.csv")
eph <- left_join(eph, lbls, by = "site")

eph$label <- as.factor(eph$label)
eph$label <- factor(eph$label, levels = c("Semi-arid 1", "Semi-arid 2", "Semi-arid 3", "Semi-arid 4", "Semi-arid 5", "Semi-arid 6", "Arid 7", "Arid 8", "Arid 9"))

c <- ggplot(eph, aes(label, Species, fill = Microsite)) + geom_boxplot() + ylab("Arthropod Richness") + theme(legend.position = "bottom", legend.box = "horizontal") + scale_fill_manual(values=c("white", "gray"))
l1 <- get_legend(c)

rdm <- left_join(rdm, lbls, by = "site")

rdm$label <- factor(rdm$label, levels = c("Semi-arid 1", "Semi-arid 2", "Semi-arid 3", "Semi-arid 4", "Semi-arid 5", "Semi-arid 6", "Arid 7", "Arid 8", "Arid 9"))

rdm$label <- as.factor(rdm$label)
eph$label <- as.factor(eph$label)

a <- ggplot(rdm, aes(label, RDM, fill = Microsite)) +  
 stat_boxplot(geom ='errorbar')+ geom_boxplot() + ylab("RDM Biomass (g)") + theme(legend.position = "none") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + stat_summary(fun=mean, colour="black", geom="point", shape=18, size=3, position=position_dodge(.8)) + scale_fill_manual(values=c("white", "gray")) + theme(legend.box = "horizontal", legend.position = c(0.9, 0.9), legend.title = element_blank())
a

b <- ggplot(rdm, aes(label, rdm.cov, fill = Microsite))  +  
 stat_boxplot(geom ='errorbar')+ geom_boxplot() + ylab("RDM Cover (%)") + theme(legend.position = "none")+ xlab("")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + stat_summary(fun=mean, colour="black", geom="point", shape=18, size=3, position=position_dodge(.8))+ scale_fill_manual(values=c("white", "gray"))


c <- ggplot(eph, aes(label, Species, fill = Microsite)) +  
 stat_boxplot(geom ='errorbar') + geom_boxplot() + ylab("Arthropod Richness") + theme(legend.position = "none")+ xlab("")+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + stat_summary(fun=mean, colour="black", geom="point", shape=18, size=3, position=position_dodge(.8))+ scale_fill_manual(values=c("white", "gray"))

d <- ggplot(filter(eph, abun < 350), aes(label, abun, fill = Microsite)) +  
 stat_boxplot(geom ='errorbar') + geom_boxplot() + ylab("Arthropod Abundance (captures/trap)") + theme(legend.position = "none") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + xlab("Site") + stat_summary(fun=mean, colour="black", geom="point", shape=18, size=3, position=position_dodge(.8))+ scale_fill_manual(values=c("white", "gray"))


plots <- list(a,b,c,d)
grobs <- list()
widths <- list()

for (i in 1:length(plots)){
    grobs[[i]] <- ggplotGrob(plots[[i]])
    widths[[i]] <- grobs[[i]]$widths[2:5]
}

maxwidth <- do.call(grid::unit.pmax, widths)
for (i in 1:length(grobs)){
     grobs[[i]]$widths[2:5] <- as.list(maxwidth)
}

p <- do.call("grid.arrange", c(grobs, ncol = 1))
p

#grid.arrange(p, l1, ncol = 1,  heights = c(1, 0.1))
```


Figure 2 RII
```{r}
full.rii <- read.csv("clean_data/fullrii.csv")
full.rii <- mutate(full.rii, ci = 1.96*error)

full.rii$response <- factor(full.rii$metric, levels = c("abun", "richness", "cov", "rdm"))
full.rii$site <- "Overall"
test <- bind_rows(rii, full.rii)

rii <- mutate(rii, ci = error*1.96)

test$response <- factor(test$response, levels = c("rdm", "cov", "richness", "abun"))

test <- left_join(test, lbls, by = "site")
test$label[is.na(test$label)] <- "Pooled Sites"

test$label <- factor(test$label, levels = c("Pooled Sites", "Semi-arid 1", "Semi-arid 2", "Semi-arid 3", "Semi-arid 4", "Semi-arid 5", "Semi-arid 6", "Arid 7", "Arid 8", "Arid 9"))
library(scales)
group.colors <- c("#000000", hue_pal()(9))
names( group.colors ) <- LETTERS[1:4]; group.colors


rii.plot <- ggplot(test, aes(x=response, y=average)) + geom_point(aes(response, average,  color = label), position = position_dodge(width = 0.7),  size=4)+ geom_errorbar(aes(ymin=average-error, ymax=average + error, color = label), width=.1, position= position_dodge(width = 0.7))  + ylim(-1, 1) + theme(axis.text.x=element_text(angle=90, vjust=.5)) + ylab("RII") + xlab("") + geom_hline(aes(yintercept=0))  + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) + scale_x_discrete(labels = c("RDM Biomass (g)", "RDM Cover (%)", "Arthropod Richness", "Arthropod Abundance \n (captures/trap)")) +  scale_colour_manual( values= group.colors, name = "Sites")+ theme(text = element_text(size = 25))

rii.plot 

#geom_errorbar(aes(ymin=average-ci, ymax=average + ci), width=.1, position= position_dodge(width = 0.5)) + geom_point(aes(metric, average), position=position_dodge(width=0.5), colour="black", fill = "black", pch=21, size=4) + ylim(1, -1) + theme(axis.text.x=element_text(angle=90, vjust=.5)) + ylab("RII") + xlab("") + geom_hline(aes(yintercept=0))  + coord_flip() 
```










Figure 3 Scatterplots/correlation coefficients

```{r}
fit1<- lm(richness ~ rdm, rel.rii)
a <- ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 0, y = 0.23),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5)))+ ylab("Mean RII Arthropod Richness") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + theme(text = element_text(size = 18))


fit1 <- lm(richness ~ cov, rel.rii)
b <- ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 0.25, y = 0.23),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5)))  + ylab("") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + theme(text = element_text(size = 18))
b


fit1 <- lm(abun ~ rdm, rel.rii)
c <- ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = -0, y = 0.65),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + xlab("Mean RII RDM Biomass") + ylab("Mean RII Arthropod Abundance") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black")) + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + theme(text = element_text(size = 18))
c

fit1 <- lm(abun ~ cov, rel.rii)
d <- ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 0.24, y = 0.65),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + xlab("Mean RII RDM cover") + ylab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + theme(text = element_text(size = 18))

d

grid.arrange(a, b, c, d, ncol = 2)
```

Figure 4 - Aridty and ESI vs RII
```{r}
#so many scatters, let's do a 3 by 2


fit1 <- filter(site.rii, response == "rdm") %>% lm(mean.rdm.biomass ~ arid,.)
a <- ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 4, y = 3.5),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + ylab("Mean RDM Biomass (g)") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + theme(text = element_text(size = 18))
a


fit1 <- filter(site.rii, response == "rdm") %>% lm(mean.rdm.biomass ~ ESI,.)
b <-  ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 0.03, y = 3.5),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + ylab("") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))
b


fit1 <- filter(site.rii, response == "rdm") %>% lm(mean.rdm.cov ~ arid,.)
c <- ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 4, y = 60),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + ylab("Mean RDM Cover (%)") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))
c


fit1 <- filter(site.rii, response == "rdm") %>% lm(mean.rdm.cov ~ ESI,.)
d <-  ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 0.03, y = 60),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + ylab("") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))
d


fit1 <- filter(site.rii, response == "rdm") %>% lm(average ~ arid,.)
e <- ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 4, y = 1),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + ylab("Mean RII RDM Biomass")+ theme(text = element_text(size = 18))
e


fit1 <- filter(site.rii, response == "rdm") %>% lm(average ~ ESI,.)
f <-  ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 0.03, y = 0.78),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + ylab("") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + theme(text = element_text(size = 18))
f

fit1 <- filter(site.rii, response == "cov") %>% lm(average ~ arid,.)
g <- ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 4, y = 0.75),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + ylab("Mean RII Cover") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))
g

fit1 <- filter(site.rii, response == "cov") %>% lm(average ~ ESI,.)
h <-  ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 0.04, y = 0.7),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + ylab("") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))
h


fit1 <- filter(site.rii, response == "richness") %>% lm(average ~ arid,.)
i <- ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 4, y = 0.24),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + ylab("Mean RII Richness") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))

i

fit1 <- filter(site.rii, response == "richness") %>% lm(average ~ ESI,.)
j <-  ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 0.03, y = 0.3),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + ylab("") + xlab("") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))
j

fit1 <- filter(site.rii, response == "abun") %>% lm(average ~ arid,.)
k <- ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 4, y = 0.8),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + xlab("Aridity") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) + ylab("Mean RII Abundance")+ theme(text = element_text(size = 18))
k


fit1 <- filter(site.rii, response == "abun") %>% lm(average ~ ESI,.)
l <-  ggplot(fit1$model, aes_string(x = names(fit1$model)[2], y = names(fit1$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  geom_label(aes(x = 0.04, y = 0.8),vjust=1, hjust = 0, 
             label = paste("Adj r2 = ",signif(summary(fit1)$adj.r.squared, 5),
 " \nP =",signif(summary(fit1)$coef[2,4], 5))) + ylab("") + xlab("Evaporative Stress Index") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))  + theme(plot.margin=grid::unit(c(0,0,0,0), "mm"))+ theme(text = element_text(size = 18))
l


#grid.arrange(a, b, c, d, e, f, g, h, i, j, k, l, ncol = 2)


plots <- list(a,b,c,d,e,f,g,h,i,j,k,l)
grobs <- list()
widths <- list()

for (i in 1:length(plots)){
    grobs[[i]] <- ggplotGrob(plots[[i]])
    widths[[i]] <- grobs[[i]]$widths[2:5]
}

maxwidth <- do.call(grid::unit.pmax, widths)
for (i in 1:length(grobs)){
     grobs[[i]]$widths[2:5] <- as.list(maxwidth)
}

p <- do.call("grid.arrange", c(grobs, ncol = 2))
p


full.rii <- mutate(full.rii, upperCI = average + ci, lowerci = average - ci)

```

Appendix figures

```{r, appendix figures}
ggplot(eph, aes(RDM, fill = Microsite)) + geom_density(alpha = 0.7) + theme_classic() + xlab("RDM (g)")
```
# Conclusions

* Ephedra signficantly influences insect abundance and richness
* Ephedra supports greater plant biomass

