---
title: Arthropod associations with residual dry matter and foundations shrubs in California
  desert ecosystems
output:
    rmdformats::readthedown:
      collapsed: false
      highlight: kate
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
library(ggthemes)

env <- read.csv("clean_data/cov.csv")
comm <- read.csv("clean_data/comm.csv")
rdm <- read.csv("clean_data/veg_covariates.csv")
eph <- filter(env, Microsite != "larrea")
```

***

Pitfall traps were deployed along an aridity gradient in California to measure associations of ground-dwelling arthropods with foundation shrubs, and to assess the ability of residual dry matter (RDM) as an indicator of arthropod community structure.

***

## Differences between sites


### Residual dry matter
```{r}
ggplot(rdm, aes(RDM)) + geom_density() + facet_grid(~site) + theme_classic()
ggplot(rdm, aes(Microsite, RDM)) + geom_boxplot() + facet_grid(~site)+ theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))

```



### Insect morphospecies richness
```{r}
ggplot(env, aes(Species, fill = Microsite)) + geom_density(alpha = 0.7) + facet_grid(~site)+ theme_classic()
ggplot(env, aes(Microsite, Species)) + geom_boxplot() + facet_grid(~site)+ theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```




### Insect abundance
There is one sample with 1200 insects in it, almost all ants that really throws everything off. 
```{r}
env %>% filter(abun < 350) %>% ggplot(aes(abun, fill = Microsite)) + geom_density(alpha = 0.7) + facet_grid(~site)+ theme_classic()

env %>% filter(abun < 350) %>% ggplot(aes(Microsite, abun)) + geom_boxplot() + facet_grid(~site)+ theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Influence of shrubs on RDM

### Does shrub size influence RDM?
```{r}
ggplot(rdm, aes(x, RDM)) + geom_smooth() + facet_grid(~site) + xlab("Shrub Width")+ theme_classic()

ggplot(rdm, aes(z, RDM)) + geom_smooth() + facet_grid(~site) + xlab("Shrub Height")+ theme_classic()

```


## Influence of RDM on insect communities

### Morphospecies richness
```{r}
ggplot(eph, aes(RDM, Species)) + geom_smooth(method = lm) + geom_point() + theme_classic()
ggplot(eph, aes(RDM, Species, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic()
ggplot(eph, aes(RDM, Species, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic() + facet_grid(~Region)

```
### Arthropod abundance
```{r}
ggplot(filter(eph, abun < 350), aes(RDM, abun)) + geom_smooth(method = lm) + geom_point() + theme_classic()

ggplot(filter(eph, abun < 350), aes(RDM, abun, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic()

ggplot(filter(eph, abun < 350), aes(RDM, abun, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic() + facet_grid(~Region)
```


## Influence of shrubs on arthropod communities
### Arthropod morphospecies richness

```{r}
ggplot(eph, aes(Microsite, Species)) + geom_boxplot() + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(eph, aes(Microsite, Species)) + geom_boxplot() + facet_grid(~Region) + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(eph, aes(Microsite, Species)) + geom_boxplot() + facet_grid(~site) + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
### Arthropod abundance
```{r}
ggplot(filter(eph, abun <350), aes(Microsite, abun)) + geom_boxplot() + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(filter(eph, abun <350), aes(Microsite, abun)) + geom_boxplot() + facet_grid(~Region) + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(filter(eph, abun <350), aes(Microsite, abun)) + geom_boxplot() + facet_grid(~site) + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



##RII Influence of shrubs on insect communities
##RII Influence of shrub on RDM
##RII insect communities on gradient


# Models
What influences insect abundance, diversity and composition?

What is the strength of plant facilitation?
Does the strength of facilitation change along the gradient?

#Summary of results

#Prey items only
