---
title: Arthropod associations with residual dry matter and foundations shrubs in California
  desert ecosystems
output:
    rmdformats::readthedown:
      collapsed: false
      highlight: kate
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
library(ggthemes)
library(glmmTMB)
library(sjPlot)

env <- read.csv("clean_data/cov.csv")
comm <- read.csv("clean_data/comm.csv")
rdm <- read.csv("clean_data/veg_covariates.csv")
eph <- filter(env, Microsite != "larrea")
```

***

Pitfall traps were deployed along an aridity gradient in California to measure associations of ground-dwelling arthropods with foundation shrubs, and to assess the ability of residual dry matter (RDM) as an indicator of arthropod community structure.

***

## Differences between sites


### Residual dry matter
```{r}
ggplot(rdm, aes(RDM)) + geom_density() + facet_grid(~site) + theme_classic()
ggplot(rdm, aes(Microsite, RDM)) + geom_boxplot() + facet_grid(~site)+ theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))

```



### Insect morphospecies richness
```{r}
ggplot(env, aes(Species, fill = Microsite)) + geom_density(alpha = 0.7) + facet_grid(~site)+ theme_classic()
ggplot(env, aes(Microsite, Species)) + geom_boxplot() + facet_grid(~site)+ theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```




### Insect abundance
There is one sample with 1200 insects in it, almost all ants that really throws everything off. 
```{r}
env %>% filter(abun < 350) %>% ggplot(aes(abun, fill = Microsite)) + geom_density(alpha = 0.7) + facet_grid(~site)+ theme_classic()

env %>% filter(abun < 350) %>% ggplot(aes(Microsite, abun)) + geom_boxplot() + facet_grid(~site)+ theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Influence of shrubs on RDM

### Does shrub size influence RDM?
```{r}
ggplot(rdm, aes(x, RDM)) + geom_smooth() + facet_grid(~site) + xlab("Shrub Width")+ theme_classic()

ggplot(rdm, aes(z, RDM)) + geom_smooth() + facet_grid(~site) + xlab("Shrub Height")+ theme_classic()

```


## Influence of RDM on insect communities

### Morphospecies richness
```{r}
ggplot(eph, aes(RDM, Species)) + geom_smooth(method = lm) + geom_point() + theme_classic()
ggplot(eph, aes(RDM, Species, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic()
ggplot(eph, aes(RDM, Species, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic() + facet_grid(~Region)

```
### Arthropod abundance
```{r}
ggplot(filter(eph, abun < 350), aes(RDM, abun)) + geom_smooth(method = lm) + geom_point() + theme_classic()

ggplot(filter(eph, abun < 350), aes(RDM, abun, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic()

ggplot(filter(eph, abun < 350), aes(RDM, abun, fill = Microsite)) + geom_smooth(method = lm) + geom_point() + theme_classic() + facet_grid(~Region)
```


## Influence of shrubs on arthropod communities
### Arthropod morphospecies richness

```{r}
ggplot(eph, aes(Microsite, Species)) + geom_boxplot() + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(eph, aes(Microsite, Species)) + geom_boxplot() + facet_grid(~Region) + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(eph, aes(Microsite, Species)) + geom_boxplot() + facet_grid(~site) + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
### Arthropod abundance


```{r}
ggplot(filter(eph, abun <350), aes(Microsite, abun)) + geom_boxplot() + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(filter(eph, abun <350), aes(Microsite, abun)) + geom_boxplot() + facet_grid(~Region) + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
ggplot(filter(eph, abun <350), aes(Microsite, abun)) + geom_boxplot() + facet_grid(~site) + theme_classic() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Site level RII 
### Residual dry matter

```{r}
rii <- read.csv("clean_data/rii.csv")
ggplot(rii, aes(arid, average, color = response)) + geom_errorbar(aes(arid, ymin = average - error, ymax = average + error)) + geom_point() + geom_jitter() 
ggplot(rii, aes(arid, average, color = response)) + geom_smooth(method = lm)

```


# Models

### Drivers of insect morphospecies abundance

```{r}
eph.abun <- filter(eph, abun < 350)
m1 <- glmmTMB(abun ~ Microsite + RDM + (1|Region/site), family = "poisson", data = eph.abun)
summary(m1)
#looks overdispersed

m1.nb <- glmmTMB(abun ~ Microsite + RDM + (1|Region/site), family = "nbinom2", data = eph.abun)
summary(m1.nb)

m1.nb1 <- glmmTMB(abun ~ Microsite + RDM + (1|Region/site), family = "nbinom1", data = eph.abun)
summary(m1.nb1)

m2 <- glmmTMB(abun ~ Microsite * RDM + (1|Region/site), family = "nbinom2", data = eph.abun)
summary(m2)

AIC(m1, m1.nb, m1.nb1)

#nbinom2 without interaction is the best
summary(m1.nb)
knitr::kable(car::Anova(m1.nb, type = 2))
```

### Insect morphospecies richness

```{r}
m1 <- glmmTMB(Species ~ Microsite + RDM + (1|Region/site), family = "poisson", data = eph)
summary(m1)

#nb models don't coverge -> likely suggests overdispersion not an issue but should add a formal check

m1.nb <- glmmTMB(Species ~ Microsite + RDM + (1|Region/site), family = "nbinom2", data = eph)

m1.nb1 <- glmmTMB(Species ~ Microsite + RDM + (1|Region/site), family = "nbinom1", data = eph.abun)


m2 <- glmmTMB(Species ~ Microsite * RDM + (1|Region/site), family = "poisson", data = eph)
summary(m2)

AIC(m1, m2)


summary(m1)
knitr::kable(car::Anova(m1, type = 2))
```

### Residual dry matter

```{r}
shapiro.test((rdm$RDM)^(1/3))
#lolz

ggplot(rdm, aes(log(RDM+1))) + geom_density()

m1 <- glmmTMB((rdm$RDM)^(1/3) ~ Microsite + (1|Region/site), family = "gaussian", data = rdm)
shapiro.test(residuals(m1))
```


#Summary of results
* Ephedra signficantly influences insect abundance and richness
* Ephedra supports greater plant biomass

#Prey items only
